\lecture{01}{Mon 06 Jan 2020 8:39}{Intro}
	
	\section{Introduction}
	\subsection{Marking Scheme}
	\begin{description}
		\item[Quizzes] 40\% in tutorial in even weeks, drop lowest score
		\item[Final Exam] 60\%. If final exam grade is <40\%, grade $=min\{final, usual\}$
	\end{description}
	
	Content of quiz 1:

	\begin{itemize}
		\item system of linear homogeneous differential equations 
		\item Scalar linear inhomogeneous differential equations 
	\end{itemize}
	
	This is a system theory course. 

	\section{General System Theory}
	
	\begin{definition}
		A general input-output system is a triple $(U, Y, B)$, where

	\begin{enumerate}
		\item $U$ is a set (the set of inputs)
		\item $Y$ is a set (the set of outputs)
		\item $B \subseteq U \times  Y$ (the behaviours).
	\end{enumerate}
	\end{definition} 
	An element of $B$ looks like $(\mu , \eta)$ with $\mu$ an input and $\eta$ an output. If $\mu \in U$ we denote 
	\[
		B(\mu) = \{(\mu, \eta) \in B\}
	.\]
	This is the set of all behaviours corresponding to $\mu \in U$. 

	\begin{definition}
		A functional input/output system is a general input/output system $(U, Y, B)$ so that $B$ is the graph of some mapping $ \Phi : u \to y $:
	\[
		B = graph(\Phi) = \{(\mu, \Phi (\mu))  \mid \mu \in  U\}
	.\] 
	\end{definition}

	\begin{description}
		\item[States:] Let $U$ be a set of inputs and let $Y$ be a set of outputs. A response function for a system $(U, Y, B)$ is a mapping 	\[
			 \rho : U \times  X  \to Y 
			.\] such that \[
			B = \{(\mu, \rho (\mu, x))  \mid \mu \in  U, x \in  X \}
			.\]
		X is called a state object. One should think of $X$ as parameterising the outputs for a fixed input. 
			
	\end{description}
	\begin{definition}
	A linear general input/output system is a general input/output system $(U, Y, B)$ such that 
	\begin{enumerate}
		\item $U$ and $Y$ are vector spaces 
		\item $B  \subseteq U \oplus Y$ is a subspace
	\end{enumerate}	
	\end{definition}
	One also has linear response functions, meaning that $U$, $Y$ and $X$ are vector spaces, and $ \rho : U \oplus X  \to Y $ is linear. 

	\begin{conclusion}
		If $(U, Y, B)$ is a linear input/output system it has a linear response function.
	\end{conclusion}
